\huge Tor's Usability for Censorship Circumvention

### 2016-10-14 pets2017-paper/pets2017-rebuttal.txt

We would like to thank the reviewers for their comments. We now will address each reviewer’s concerns:

7A:
- We will clarify that our experiments may be most applicable to novice Tor users. We expect our participants were adequately motivated to complete the task, due to the Hawthorne effect (i.e., they knew they were being observed completing the tasks). We will acknowledge that we have not studied international users. 
- The success rate improvement is indeed not statistically significant; see Section 8.4.1, sentence 2. We will revise to clarify that our primary contribution is in reducing the time it takes to configure Tor.

7B:
- The purpose of the quantitative study was to evaluate the impact of our proposed changes. A qualitative study can only identify a breadth of potential usability problems, but not their prevalence. 
- We obtained informed consent from all participants, warned them that they were being recorded (see Appendix G), and obtained IRB approval.
- We agree that we need to greatly expand Related Work. We will add discussion of how our findings relate to heuristics in the general usability literature.

7C:
-Our work is unique in that we study previously unexplored concepts (bridges and pluggable transports), and heavily favor minimizing any behaviors that reveal to a passive network eavesdropper that users are connecting to Tor. 
-We will detail what we learned from the pluralistic walkthrough and heuristic evaluation, including how participants behaved (based on the videos) and their responses to the interview questions. We omitted this because the insights largely overlap with what we learned from the other methods.
- We agree that studying real censorship environments would increase external validity; however, it makes it more difficult to eliminate potential confounds, more difficult to characterize the censorship environment, and thus more challenging to assess how results from one location might apply to another.
- Full automation introduces complex ethical and security considerations (see Section 10), not all of which are solely technical. To increase the likelihood that our proposals are adopted by the Tor project, the scope of this work is focused on UI improvements. This scope was informed by discussions with numerous Tor developers.

7D:
-Quotes are based on our notes from the interviews and are not verbatim since we did not record voices (PII). We stopped participants after 45 minutes. 
- We picked wikipedia and CNN because they are 1) websites from the Alexa 100 that 2) do not require personal information , and 3) are commonly blocked by censors. 
- We know the UI was designed with user’s agency in mind based on Tor developers who strongly oppose automating the process (personal conversations; see also https://trac.torproject.org/projects/tor/ticket/10418#comment:18, https://trac.torproject.org/projects/tor/ticket/10538#comment:3, https://lists.torproject.org/pipermail/tor-dev/2015-May/008790.html).
- We will revise the discussion of Related Work to better clarify the relationship to prior work.

We will revise to correct the issues regarding typos, organization, clarity, causal implications, and rephrasing mentioned by 7C and 7D. We believe that most of the issues raised can be fixed with a minor revision/shepherding.

### 2016-10-14 pets2017-paper/pets2017-paper.tex
pass through introduction; de-emphasize censorship, add clairity.

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability in this role.
We evaluate, design, and test the Tor configuration interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative user study tests the impact of our changes.
We find that our changes result in a significant reduction 
in the time spent configuring a connections. We
conclude with recommendations for changes to the current interface as well as 
alternative approaches to bootstrapping a connection to Tor.}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

>>>>

  \begin{abstract}
{
We evaluate, design, and test the Tor configuration interface by
placing users in simulated censorship environments, instructing them to use Tor
to circumvent censorship, and measuring their interface interactions.
A 16-participant qualitative study examines user assumptions and common mistakes.
We use the results as feedback to redesign the configuration interface.
A 114-participant quantitative study shows that our design changes result in
a significant reduction in time. We conclude with recommendations for changes 
to the current interface as well as alternative solutions.}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}
